Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
write on invariance to translation

\section{Scattering transforms}
The scattering transform is a multiscale representation of audio signals which cascades an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.

>>>>

\section{Scattering transforms}
Scattering transforms are a multiscale representations of audio signals which cascade an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.

The notion of invariance to translation plays an essential role in auditory scene classification.
Indeed, the starting time of the recordings are chosen arbitrarily, and thus do not convey any information about the class.
To cancel this superfluous source of variability, signals must be mapped to a translation-invariant feature space prior to training a classifier.
